Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2018-01-05 WSSSPE4_report/WSSSPE4_paper.tex
adding comments from Reviewer B in conclusions - still need to deal with them

>>>>

\textcolor{red}{comments from reviewer B to discuss: Finally, in a similar vein, the summary and conclusion offers very little in terms of synthesis of main themes that arose during the meeting. The reader is left to synthesize the diversity of sections 4 and 5, that discuss the main activities of the workshop itself, on their own. It may very well be that the workshop is diverse enough in terms of its topics (and indeed, it does seem like there are a lot of very interesting topics, and a lot of interesting work done as part of the workshop!), but surely there is some over- arching themes that could be summarized? Instead, the conclusion is that a workshop such as this is unlikely to produce tangible work in the long run, because participants are reluctant to commit to additional activities, above and beyond these undertaken during the workshop. While this seems like an honest (if disappointing?) conclusion, it is also difficult to reconcile with the multiple places in which the authors ask interested parties to join Slack channels and mailing lists. Maybe the expectation that a few hours of joint work at a workshop would lead to a committed collaboration with other participants is too high? Rather, expectations from conferences and workshops are usually much lower: exchanging ideas, establishing and broadening a professional network, and learning about work that is being done in the field. Maybe it?s enough if these goals are achieved at WSSSPE as well?}
